\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-03 paper/main.tex
illustrative example walkthrough through line 4

>>>>

After importing \texttt{davos} (line 1), the user first smuggles two utilities for checking and reading local files in the code below. The \texttt{smuggle} statement in line 3 loads the \texttt{is\_file()} function from the Python standard library's \texttt{os.path} module. Standard library modules are included with all Python distributions, so this line is functionally equivalent to an \texttt{import} statement and no onion comment is needed. Line 4 loads the \texttt{joblib} library~\cite{Varo10}, installing it first, if necessary. Since \texttt{joblib}'s I/O interface has historically remained stable and backwards-compatible across releases, requiring that users have a particular exact version installed would likely be unnecessarily restrictive. However, there's also no guarantee that a \textit{future} release won't introduce some breaking change, so to help ensure the analysis notebook continues to run properly in the future, the onion comment in line 4 limits allowable versions to those already released when the code was written.
%After importing \texttt{davos} (line 1), the user first smuggles two utilities that will be used to help find and load local files in the code below: the \texttt{is\_file} function from the \texttt{os.path} module, and the \texttt{joblib} library~\cite{Varo10} (lines 3--4). The first \texttt{smuggle} statement needs no onion comment, as the \texttt{os.path} module is part of Python's standard library and is therefore guaranteed to be available. The second ensures \texttt{joblib} is installed before loading it Enforcing an exact version of \texttt{joblib} is likely unnecessary, since the package's I/O interface has historically remained generally stable across versions. However, there's no
